\documentclass{article} % 

% Per la sottomissione anonima, usa questa riga:
% \usepackage{neurips_2024} % 
% Per la versione preprint (su arXiv) usa:
\usepackage[preprint]{neurips_2024} % [cite: 1, 20]
% Per la versione finale usa:
% \usepackage[final]{neurips_2024} % [cite: 1, 23]

\usepackage[utf8]{inputenc} % allow utf-8 input 
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts 
\usepackage{hyperref}       % hyperlinks 
\usepackage{url}            % simple URL typesetting [cite: 1, 2]
\usepackage{booktabs}       % professional-quality tables [cite: 2]
\usepackage{amsfonts}       % blackboard math symbols [cite: 2]
\usepackage{nicefrac}       % compact symbols for 1/2, etc. [cite: 2]
\usepackage{microtype}      % microtypography [cite: 2]
\usepackage{xcolor}         % colors [cite: 2]
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs} % For \toprule, \midrule, \bottomrule
\usepackage{multirow} % For the vertical grouped text in Table 5
\usepackage{graphicx} % For \rotatebox

\title{Decision Focused Learning Via Neural Operators} % [cite: 293, 294]

% Autori con formattazione classica a numeri
\author{%
  Francesco Giordani\textsuperscript{1} \quad 
  Davide Evangelista\textsuperscript{1} \quad 
  Michele Lombardi\textsuperscript{1} \\
  \textsuperscript{1}University of Bologna
}

\begin{document}

\maketitle

\begin{abstract}

\textit{What is the studied problem and why is it important?}\\
We study the Predict-then-Optimize (PtO) framework, often used in decision support systems. Before solving an optimization problem, these systems require to predict some unknown parameters relative to the optimization problem.

\textit{What are the main limitations of the existing solutions?}\\
The prediction of these parameters has been shown to be suboptimal using traditional learning estimators. 
To overcome this issue, Decision Focused Learning (DFL) has been proposed, directly optimizing the decision quality of this two-stage process through a decision loss. 
However, training DFL methods is inherently difficult due to the lack of the gradient and the computational cost of solving NP-hard optimization problems.

\textit{What are the proposed solution and its advantages?}\\
In this paper, we propose to dolve all the major issues of DFL under very mild assumption relying on Neural Operators \dots.

\textit{How does the proposed solution work?}\\
The proposed method works by \dots.

\textit{What is the major finding?}\\
The major finding is that \dots.

\end{abstract}

\input{sections/introduction.tex}
\input{sections/related_work.tex}
\input{sections/problem_formulation.tex}
\input{sections/methodology.tex}
\input{sections/experiments.tex}
\input{sections/conclusions.tex}

\begin{ack}
\end{ack}

\bibliographystyle{plainnat}
\bibliography{references}

\newpage
\section*{NeurIPS Paper Checklist}

\end{document}